---
title: "wind_tunnel2"
author: "Maxwel Coura Oliveira"
date: "2/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(ggtext)
library(tidytext)
library(ggthemes)
library(broom)
library(patchwork)
```


```{r}
data <- read.csv("windtunnel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate_if(is_character, as_factor) %>% 
  mutate(orifice_size = as_factor(orifice_size))
```


```{r linear-model}
lm_mod <- 
  linear_reg() %>% 
  set_engine("lm")
```

# Drifable fines

```{r}
lm_fit_drift <-
  lm_mod %>% 
  fit(fines_200 ~ nozzle * solution_name * orifice_size * pressure, data = data)
```

# dv50

```{r}
lm_fit_dv <- 
  lm_mod %>% 
  fit(dv50 ~ nozzle * solution_name * orifice_size * pressure, data = data)

```


```{r}
new_points <- expand.grid(pressure = 40,
                          solution_name = unique(data$solution_name),
                        orifice_size = c("0.3", "0.4", "0.5", "0.6"),
                        nozzle = unique(data$nozzle)) %>% 
  mutate(sol_number = as.numeric(solution_name)) %>% 
  dplyr::select(sol_number, solution_name, everything()) 
```


```{r}
#Getting predited values
mean_pred_drift <- predict(lm_fit_drift, new_data = new_points)
mean_pred_dv <- predict(lm_fit_dv, new_data = new_points)
```


```{r}
#Getting conf intervals
conf_int_pred_drift <- predict(lm_fit_drift, 
                         new_data = new_points, 
                         type = "conf_int")


conf_int_pred_dv <- predict(lm_fit_dv, 
                         new_data = new_points, 
                         type = "conf_int")
```

```{r}
data1 <- 
  new_points %>% 
  bind_cols(mean_pred_drift) %>% 
  bind_cols(conf_int_pred_drift)

data2 <- 
  new_points %>% 
  bind_cols(mean_pred_dv) %>% 
  bind_cols(conf_int_pred_dv)

category <- data %>% 
  filter(pressure == 40) %>% 
  distinct(solution_name, nozzle, orifice_size, pressure, category)

data3 <- data1 %>% 
  dplyr::select(.pred) %>% 
  rename(driftable = .pred) %>% 
  bind_cols(data2) %>% 
  left_join(category) %>% 
  filter(!is.na(category))
```



```{r}
data4 <- data3 %>% 
         mutate(solution_name = fct_relevel(solution_name, 
                                  levels = c("water", 
                                             "glyphosate", 
                                             "dicamba", 
                                             "dicamba+glyphosate",
                                             "dicamba+glyphosate+dra1",
                                             "dicamba+glyphosate+dra2", 
                                             "dicamba+glyphosate+clethodim+dra1",
                                             "dicamba+glyphosate+clethodim+dra2",
                           "dicamba+glyphosate+clethodim+acetochlor+dra1",
                           "dicamba+glyphosate+clethodim+acetochlor+dra2",
                           "dicamba+glyphosate+clethodim+s-metolachlor+dra1",
                           "dicamba+glyphosate+clethodim+s-metolachlor+dra2", 
                           "dicamba+glyphosate+glufosinate",
                           "dicamba+glyphosate+glufosinate+dra1",
                           "dicamba+glyphosate+glufosinate+dra2",
                           "dicamba+glyphosate+glufosinate+clethodim+dra1",
                           "dicamba+glyphosate+glufosinate+clethodim+dra2"))) %>% 
  mutate(solution_name = fct_recode(solution_name,
                                  "water" = "water", 
                                  "glyphosate" =  "glyphosate", 
                                  "dicamba" =   "dicamba", 
                                  "dicamba + glyphosate" = "dicamba+glyphosate",
                                  "dicamba + glyphosate + DRA 1" = "dicamba+glyphosate+dra1",
                                  "dicamba + glyphosate + DRA 2" = "dicamba+glyphosate+dra2", 
                                  "dicamba + glyphosate + clethodim + DRA 1" = "dicamba+glyphosate+clethodim+dra1",
                                  "dicamba + glyphosate + clethodim + DRA 2" = "dicamba+glyphosate+clethodim+dra2",
                                  "dicamba + glyphosate + clethodim + acetochlor + DRA 1" = "dicamba+glyphosate+clethodim+acetochlor+dra1",
                                  "dicamba + glyphosate + clethodim + acetochlor + DRA 2" = "dicamba+glyphosate+clethodim+acetochlor+dra2",
                                  "dicamba + glyphosate + clethodim + *S*-metolachlor + DRA 1" = "dicamba+glyphosate+clethodim+s-metolachlor+dra1",
                                  "dicamba + glyphosate + clethodim + *S*-metolachlor + DRA 2" = "dicamba+glyphosate+clethodim+s-metolachlor+dra2", 
                                  "dicamba + glyphosate + glufosinate" = "dicamba+glyphosate+glufosinate",
                                  "dicamba + glyphosate + glufosinate + DRA 1" = "dicamba+glyphosate+glufosinate+dra1",
                                  "dicamba + glyphosate + glufosinate + DRA 2" = "dicamba+glyphosate+glufosinate+dra2",
                                  "dicamba + glyphosate + glufosinate + clethodim+ DRA 1" = "dicamba+glyphosate+glufosinate+clethodim+dra1",
                                  "dicamba + glyphosate + glufosinate + clethodim + DRA 2" = "dicamba+glyphosate+glufosinate+clethodim+dra2"))
```




```{r message = FALSE, warning=FALSE}
library(extrafont)
library(ggtext)
#extrafont::loadfonts()

font_family <- 'Helvetica'
title_family <- "Arial Black"
legend_family <- "Comic Sans MS"
subtitle_family = "Arial"
background <- "#1D1D1D"
text_colour <- "white"
axis_colour <- "white"
plot_colour <- "white"

theme_style <- theme(axis.text.x = element_text(angle = 45, hjust = 1, 
                                                size = 12, color = "black",
                                                family = subtitle_family),
        axis.text.y = element_text(size = 12, family = subtitle_family, color = "black"),
        axis.title.x = element_text(size = 13, face = "bold",  family = subtitle_family),
        plot.title.position = "plot",
        plot.title = element_markdown(vjust = 2, size = 20, 
                                  family = subtitle_family, margin = margin(2,1,1,1)),
        plot.subtitle = element_markdown(vjust = 2, size = 12, family = subtitle_family),
        plot.caption = element_text(size = 9, family = subtitle_family, hjust = 0),
        axis.ticks.x = element_blank(),
        legend.text = element_text(family = subtitle_family),
        legend.title = element_markdown(family = subtitle_family, size =12, face = "bold"),
        legend.position = "bottom",
        legend.box = "horizontal",
        legend.direction = "horizontal",
        legend.background = element_blank(),
        legend.box.background = element_blank(),
        legend.key = element_blank(),
        panel.background = element_rect(fill = plot_colour),
        plot.background = element_rect(fill = plot_colour),
        strip.text = element_markdown(size = 13, face = "bold"))

theme_set(theme_bw() + theme_style)
```

expression(paste("% of predicted drifable fines (< 200 ", mu, "m)"))

```{r}
library(ggtext)
f1 <- data4 %>% 
  filter(pressure == "40") %>% 
  ggplot(aes(x = solution_name, y = .pred, color = category)) +
  geom_point(size = 1) +
  facet_grid(nozzle ~ orifice_size) +
  geom_point(aes(size = driftable), alpha = 0.4) +
  scale_size_continuous(
                        limits = c(1, 6), breaks=c(1, 2, 3, 4, 5, 6),
                        guide = guide_legend(title.position = "top", nrow = 1)) +
  scale_x_discrete(limits = rev) +
  scale_color_manual(name = "Nozzle category", values = c("red", "blue"),
                        guide = guide_legend(title.position = "top", nrow = 1)) +
  geom_errorbar(aes(ymin = .pred_lower, 
                    ymax = .pred_upper),
                width = .2) +
  labs(x = "", y = "dv50", title = "TEST &mu;",
       size = "of predicted drifable fines (< 200 μm)") +
  coord_flip() +
  ggsave("figure.pdf", width = 14, height = 18)
```



```{r}
library(ggplot2)

ggplot(mtcars) +
  aes(mpg, disp) +
  geom_point() +
  labs(title = "TEST μ",
       x = "*abc* α",
       y = "**bold β**") +
  theme(plot.title = element_markdown(),
        axis.title.x = element_markdown(),
        axis.title.y = element_markdown())
```

